%% start of file `template.tex'.
%% Copyright 2006-2010 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[11pt,letterpaper,sans]{moderncv}

% moderncv themes
\moderncvtheme[blue]{classic}                 % optional argument are 'blue' (default), 'orange', 'red', 'green', 'grey' and 'roman' (for roman fonts, instead of sans serif fonts)
%\moderncvtheme[green]{classic}                % idem

% character encoding
\usepackage[utf8]{inputenc}                   % replace by the encoding you are using

% adjust the page margins
\usepackage[scale=0.80, vmargin=0.5in]{geometry}
%\setlength{\hintscolumnwidth}{3cm}						% if you want to change the width of the column with the dates
%\AtBeginDocument{\setlength{\maketitlenamewidth}{6cm}}  % only for the classic theme, if you want to change the width of your name placeholder (to leave more space for your address details
\AtBeginDocument{\recomputelengths}                     % required when changes are made to page layout lengths

% personal data
%https://answers.launchpad.net/moderncv/+question/128655
\firstname{Ibrahim}
\familyname{Awwal}
% \address{}{San Diego, CA 92092}    % optional, remove the line if not wanted
\mobile{925-271-7003}                    % optional, remove the line if not wanted
\email{iawwal@ucsd.edu}                      % optional, remove the line if not wanted
\homepage{ibrahim.io}

\nopagenumbers{}                             % uncomment to suppress automatic page numbering for CVs longer than one page
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
\maketitle

\section{Education}
\cventry{Fall 2013-- Present}{Phd Student, Electrical and Computer Engineering}{University of California, San Diego}{Concentration: Intelligent Systems, Robotics, and Control}{}{GPA: 3.30}  % arguments 3 to 6 can be left empty
\cventry{Fall 2008-- Spring 2012}{Bachelor of Science, Electrical Engineering and Computer Science}{\newline University of California, Berkeley}{}{}{GPA: 3.79}  % arguments 3 to 6 can be left empty

\section{Relevant Coursework}
\cvline{Graduate}{Statistical Learning, Parameter Estimation, Digital
  Signal Processing, Digital Image Processing, Random Processes,
  Convex Optimization, Machine Learning, Robotics, Computer Vision,
  Embedded Systems, Compressed Sensing} \cvline{Undergraduate}{Digital
  Design, Computer Architecture, Digital Integrated Circuits,
  Microelectronic Devices and Circuits, Machine Structures,
  Mechatronic Design, Feedback Control, Signals and Systems, Computer
  Graphics, Artificial Intelligence}

\section{Research}
\cventry{February 2015-Present}{Mobile Devices}{University of
  California, San Diego}{La Jolla}{CA}{Characterization and
  analysis of current and future user workloads, with an emphasis on the
  memory subsystem, for mobile devices. PI: Professor Tajana Rosing.
}
\cventry{January--June 2014}{Brain Machine Interfaces}{University of
  California, San Diego}{La Jolla}{CA}{Worked on analyzing
  micro-electocorticography signals for use in prosthetic devices.
  PI: Professor Vikash Gilja.}
\cventry{Sept 2010--Dec
  2012}{Undergraduate Researcher}{University of California,
  Berkeley}{Berkeley}{CA}{Personal robotics research in Professor
  Pieter Abbeel's PR2 lab. Worked on automating laundry related tasks
  and motion planning using convex optimization.}

\section{Teaching}
\cventry{March--June 2014}{CSE 20 TA}{University of California, San
  Diego}{La Jolla}{CA}{Introduction to Discrete Math for Computer Science.}

\cventry{Sept--Dec 2014}{CSE 103 TA}{University of California, San
  Diego}{La Jolla}{CA}{Introduction to Probability and
  Statistics. Taught and developed software for analyzing students'
  mistakes, including parsing and front end web development.}

\cventry{Jan--May 2012}{EE40 Head Lab TA}{University of California,
  Berkeley}{Berkeley}{CA}{Introduction to Microelectronic
  Circuits. Managed other lab TAs, served as the interface between
  instructor, TAs, students. Also coordinated logistics with local
  vendors for final project where students built an EEG amplifier
  board.}

\cventry{Aug--Dec 2011}{EE20n
  TA}{University of California, Berkeley}{Berkeley}{CA}{Teaching
  assistant for EE20n, Structure and Interpretation of Signals and
  Systems, focused on teaching signals and systems using Labview
  software.}

\section{Work Experience}
\cventry{May--Aug 2012, Jan--Aug 2013}{Full Stack Software
  Engineer}{Gradescope}{Berkeley}{CA}{Initial lead developer for
  Gradescope, an online web application for facilitating exam
  grading. Worked on frontend, backend, and devops related tasks}
\cventry{Aug--Sept 2012}{Front End Engineer}{edX}{Cambridge}{MA}{Developed discussion forum front end software for edX.org's initial launch.}

\cventry{June--Aug 2010}{Intern}{Lawrence Livermore National
  Lab}{Livermore}{CA}{Researched and implemented algorithms for
  detecting duplicate passages in large bodies of text, using Hadoop
  MapReduce and HBase.}%
% Publications
\nocite{*}
\bibliographystyle{plain}
\bibliography{publications} % 'publications' is the name of a BibTeX file

\section{Projects}
\cvline{32 bit CPU}{\small Designed and implemented a 3 stage pipelined MIPS CPU on FPGA for CS150, Digital Design}
\cvline{SRAM Array}{\small Design, schematic, and layout of a 16x20 (5 bit word) SRAM array, address decoder, and flash ADC decoder using Cadence tools. Optimized for low power and speed.}

\section{Skills}
\cvitem{Languages}{Matlab, Java, C, C++, Python, Ruby, Bash, Lisp, \LaTeX}
\cvitem{Software}{Cadence Virtuoso, SPICE, Xilinx, ROS, Git, Linux, Labview}
\cvitem{Web}{AngularJS, Backbone.js, React, Bower, Grunt, Ruby on Rails, Django, Ansible, AWS}
\section{Honors}
\cvline{Powell Fellow}{Recipient of Powell Graduate Fellowship from the UCSD ECE department}
\end{document}

%% end of file `template_en.tex'.

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
